Paper \#ZW10157

### 2019-01-17 paper/submission/ZW10157-response-1.tex
more edits to response 1
cosmetics

At the same time, AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
model embedded into a multi-objective optimization framework. In this way, optimization of various 
machine configurations can be done at different charge levels. While other codes such as GPT~\cite{gpt} and ELEGANT~\cite{borl:00}, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e. free to use), massively parallel, and fully 3D.
}

@@

\vspace{5em}

@@

{\bf Our response:}{\color{blue} 	
	We have removed all opal related code, and shortened these sections.
	Additional references now point out ELEGANT and GPT have built in genetic optimization.
}

@@

{\bf Our response:}{\color{blue} 	
	We hope the additions above are addressing these issues. }

@@

{\bf Our response: } {\color{red} This section has been shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimization algorithms. Something that you can not find in most of the 
existing codes.}

>>>>

At the same time, AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
model embedded into a multi-objective optimization framework. In this way, optimization of various 
machine configurations can be done at different charge levels. While other codes such as GPT  and ELEGANT, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e. free to use), massively parallel, and fully 3D.
}

@@

\vspace{1em}

@@

{\bf Our response: }{\color{blue} We have removed all opal related code, and shortened these sections.
	Additional references now point out ELEGANT and GPT have built in genetic optimization.}

@@

{\bf Our response: }{\color{blue} 	
	We hope the additions above are addressing these issues. }

{\bf Our response:} {\color{blue} New references were added to address this.}

{\bf Our response: } {\color{blue} This section has been shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimization algorithms. Something that you can not find in most of the 
existing codes.}

=======
\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

With the best regards  \\[3mm]

{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.}

{\bf Our response:} {\color{red} The AWA is a high charge charge accelerator. The strong non-linearities
justifying the full 3D approach. At the same time AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was one of the important research objectives, to come up with a precise, e.g. 3D
model embedded into a multi-objective optimisation framework. The OPAL framework, differentiates itself, being massively paralle,
full 3D and, and simple to use i.e.\ user friendly.}

{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
	Especially the following:

	We thank the reviewer for the list of references. 
	References described or referenced by A. Hofler in the above were excluded from 
	the bibliography. 
}

1) References for 4 PISA-based optimization systems:

{\color{blue}{Included in updated bib:}}

{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}

2) Optimization systems using NSGA-II (a few example references):

M. Borland et al. PAC 2009, Vancouver, BC, Canada, May 2009, TH6PFP062

3) Survey with various references showing GA/EA usage in Accelerator
Physics: A. Hofler. “Genetic Algorithms and Their Applications in
Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1

{\bf Our response:} {\color{red} The statements on the lines  17-19 of our initial submission are misleading, as
the referee correctly recognised. We replace them with the following:

Despite the great success of on-line models, and various model dependent and model independent tuning and 
optimisation techniques, in research facilities such as AWA empirical tuning is still one of the methods used. Due to the 
non-linear problem mainly from space charge, simple and fast models are applicable only in a very 
restricted manner. When it comes to multi-objective optimisation then the situation is even more complicated.
}

{\bf Our response:} {\color{blue} XXXXX.}

That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design. For example, in the main text, it is
reasonable to say that the optimization system provides a flexible and
extensible meta-language for setting up optimization problems (covered
in detail in Section III subsection E) and then direct the reader to
an Appendix or the Supplemental Material for the details provided in
Section III subsection E. Bear in mind, though, that several of the
PISA-based systems mentioned above, also, provide expression
capabilities and should be referenced. The one presented here is more
flexible and has the advantage of being easily extended. Both are
distinguishing features. The authors need to emphasize what
differentiates their system from 13+ years of development in the area
of GA/EA-based optimization in accelerator design and then demonstrate
that the results produced are exemplary or could not have been
produced otherwise. Or they should focus on how their system advances
the application of the target AWA machine (the Gulliford references
use this approach).

@@

{\bf Our response: } {\color{red} This section has being shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimisation algorithms. Something that you can not find in most of the 
existing codes.}`
